\textit{Supplementary materials for}: Carryover effects in free recall reveal how prior experiences influence memories of new experiences

### 2023-01-05 paper/main.tex
added example lists from each experimental conditions (in the FRFR figure).  working on methods (still...).   - also added maddy as an author (yay!)

\title{Carryover effects in free recall reveal how prior experiences influence memories of new experiences}
\author{Jeremy R. Manning\textsuperscript{1, *}, Andrew C. Heusser\textsuperscript{1, 2}, Kirsten Ziman\textsuperscript{1, 3},\\Emily Whitaker\textsuperscript{1}, and Paxton C. Fitzpatrick\textsuperscript{1}\\\textsuperscript{1}Dartmouth College\\\textsuperscript{2}Akili Interactive\\\textsuperscript{3}Princeton University\\\textsuperscript{*}Corresponding author: jeremy.r.manning@dartmouth.edu}

@@

Participants were assigned to experimental conditions based loosely on their
date of participation. (This aspect of our procedure helped us to more easily
synchronize the experiment databases across multiple testing computers.) Of the
490 participants who opted to fill out the demographics survey, reported ages
ranged from 17 to 31 years (mean: 19.1; standard deviation: 1.356). A total of
318 participants reported their gender as female, 170 as male, and 2
participants declined to report their gender. A total of 442 participants
reported their ethnicity as ``not Hispanic or Latino,'' 39 as ``Hispanic or
Latino,'' and 9 declined to report their ethnicity. Participants reported their
races as White (345 participants), Asian (120 participants), Black or African
American (31 participants), American Indian or Alaska Native (11 particiapnts),
Native Hawaiian or Other Pacific Islander (4 participants), Mixed race (3
participants), Middle Eastern (1 participant), and Arab (1 participant). A
total of 5 participants declined to report their race. We note that several
participants reported more than one of racial category. Participants reported
their highest degrees achieved as ``Some college'' (359 participants), ``High
school graduate'' (117 participants), ``College graduate'' (7 participants),
``Some high school'' (5 participants), ``Doctorate'' (1 participant), and
``Master's degree'' (1 participant). A total of 482 participants reported no
reading impairments, and 8 reported mild reading impairments such as mild
dyslexia. A total of 489 participants reported having normal color vision and 1
participant reported that they were color blind. A total of 482 participants
reported taking no prescription medications and having no recent injuries; 4
participants reported having ADHD, 1 reported having dyslexia, 1 reported
having allergies, 1 reported a recently torn ACL/MCL, and 1 reported a
concussion from several months prior. The participants reported consuming 0 --
3 cups of coffee prior to the testing session (mean: 0.32 cups; standard
deviation: 0.58 cups). Participants reported their current level of alertness,
and we converted their responses to numerical scores as follows: ``very
sluggish'' (-2), ``a little sluggish'' (-1), ``neutral'' (0), ``a little
alert'' (1), and ``very alert'' (2). Across all participants, the full range of
alertness levels were reported (range: -2 -- 2; mean: 0.35; standard deviation:
0.89) .

@@

Our experiment is a variant of the classic free recall paradigm that we term
\textit{feature-rich free recall}. In feature-rich free recall, participants
study 16 lists, each comprised of 16 words that vary along a number of stimulus
dimensions: semantic category, object size, text color, text location, word
length, and starting letter (Fig.~\ref{fig:exp}). Each list contains four words
from each of four different semantic categories and two object sizes; all other
stimulus features are randomized. After studying each list, the participant
attempts to recall as many words as they can from that list, in any order they
choose. Because each individual word is associated with several well-defined
(and quantifiable) features, and because each list incorporates a diverse mix
of feature values along each dimension, this allows us to evaluate
participants' memory fingerprints in rich detail.

\begin{figure} 
    \centering
        \includegraphics[width=0.75 \textwidth]{figures/FRFR}

        \caption{\textbf{Feature-rich free recall.} After studying lists
comprised of words that vary along several feature dimensions, participants
verbally recall words in any order (microphone icon).}

@@

@@

\paragraph{Feature dimensions.}

>>>>

\title{Carryover effects in free recall reveal how prior experiences influence memories of new experiences}
\author{Jeremy R. Manning\textsuperscript{1, *}, Kirsten Ziman\textsuperscript{1, 2}, Emily Whitaker\textsuperscript{1},\\Paxton C. Fitzpatrick\textsuperscript{1}, Madeline R. Lee\textsuperscript{1}, and Andrew C. Heusser\textsuperscript{1, 3}\\\textsuperscript{1}Dartmouth College\\\textsuperscript{2}Princeton University\\\textsuperscript{3}Akili Interactive\\\textsuperscript{*}Corresponding author: jeremy.r.manning@dartmouth.edu}

@@

Participants were assigned to experimental conditions based loosely on their
date of participation. (This aspect of our procedure helped us to more easily
synchronize the experiment databases across multiple testing computers.) Of the
490 participants who opted to fill out the demographics survey, reported ages
ranged from 17 to 31 years (mean: 19.1; standard deviation: 1.356). A total of
318 participants reported their gender as female, 170 as male, and 2
participants declined to report their gender. A total of 442 participants
reported their ethnicity as ``not Hispanic or Latino,'' 39 as ``Hispanic or
Latino,'' and 9 declined to report their ethnicity. Participants reported their
races as White (345 participants), Asian (120 participants), Black or African
American (31 participants), American Indian or Alaska Native (11 particiapnts),
Native Hawaiian or Other Pacific Islander (4 participants), Mixed race (3
participants), Middle Eastern (1 participant), and Arab (1 participant). A
total of 5 participants declined to report their race. We note that several
participants reported more than one of racial category. Participants reported
their highest degrees achieved as ``Some college'' (359 participants), ``High
school graduate'' (117 participants), ``College graduate'' (7 participants),
``Some high school'' (5 participants), ``Doctorate'' (1 participant), and
``Master's degree'' (1 participant). A total of 482 participants reported no
reading impairments, and 8 reported mild reading impairments such as mild
dyslexia. A total of 489 participants reported having normal color vision and 1
participant reported that they were color blind. A total of 482 participants
reported taking no prescription medications and having no recent injuries; 4
participants reported having ADHD, 1 reported having dyslexia, 1 reported
having allergies, 1 reported a recently torn ACL/MCL, and 1 reported a
concussion from several months prior. The participants reported consuming 0 --
3 cups of coffee prior to the testing session (mean: 0.32 cups; standard
deviation: 0.58 cups). Participants reported their current level of alertness,
and we converted their responses to numerical scores as follows: ``very
sluggish'' (-2), ``a little sluggish'' (-1), ``neutral'' (0), ``a little
alert'' (1), and ``very alert'' (2). Across all participants, the full range of
alertness levels were reported (range: -2 -- 2; mean: 0.35; standard deviation:
0.89).

@@

Our experiment is a variant of the classic free recall paradigm that we term
\textit{feature-rich free recall}. In feature-rich free recall, participants
study 16 lists, each comprised of 16 words that vary along a number of stimulus
dimensions (Fig.~\ref{fig:exp}). The stimulus dimensions include two semantic
features related to the \textit{meanings} of the words (semantic category,
referrent object size), two lexicographic features related to the
\textit{letters} that make up the words (word length in number of letters,
identity of the word's first letter), and two visual features that are
independent of the words themselves (text color, presentation location). Each
list contains four words from each of four different semantic categories and
two object sizes; all other stimulus features are randomized. After studying
each list, the participant attempts to recall as many words as they can from
that list, in any order they choose. Because each individual word is associated
with several well-defined (and quantifiable) features, and because each list
incorporates a diverse mix of feature values along each dimension, this allows
us to evaluate participants' memory fingerprints in rich detail.

\begin{figure}[tp]
    \centering
        \includegraphics[width=\textwidth]{figures/FRFR}

\caption{\textbf{Feature-rich free recall.} After studying lists comprised of
words that vary along several feature dimensions, participants verbally recall
words in any order (microphone icon). Each experimental condition manipulates
word features and/or presentation orders within and/or across lists. The rows
display representative (illustrated) examples of the first lists participants
might encounter in each condition. The rectangles during the ``Presentation
phase'' show illustrated screen captures during a series of word presentations.
Each word appeared onscreen for 2 seconds, followed by 2 seconds of blank
screen. The red microphone icons during the ``Recall'' phase denote the one
minute verbal recall interval.  The labels on the right (and corresponding groupings on the left)
denote experimental condition labels.}

@@

We used four ``control'' conditions to evaluate and explore participants'
baseline behaviors. We also used performance on these control conditions to
help interpret performance in other ``manipulation'' conditions. Two control
conditions served as ``anchorpoints.'' In the first anchorpoint condition,
which we call the \textit{feature rich} condition, we randomly shuffled the
presentation order (independently for each participant) of the words on each
list. The second anchorpoint condition

@@

### 2023-01-05 paper/supplement.tex
added example lists from each experimental conditions (in the FRFR figure).  working on methods (still...).   - also added maddy as an author (yay!)

@@

\title{\textit{Supplementary materials for}: Carryover effects in free recall reveal how prior experiences influence memories of new experiences}
\author{Jeremy R. Manning\textsuperscript{1, *}, Andrew C. Heusser\textsuperscript{1, 2}, Kirsten Ziman\textsuperscript{1, 3},\\Emily Whitaker\textsuperscript{1}, and Paxton C. Fitzpatrick\textsuperscript{1}\\\textsuperscript{1}Dartmouth College\\\textsuperscript{2}Akili Interactive\\\textsuperscript{3}Princeton University\\\textsuperscript{*}Corresponding author: jeremy.r.manning@dartmouth.edu}
\date{}

>>>>

\doublespacing

@@

\title{\textit{Supplementary materials for}: Carryover effects in free recall reveal how prior experiences influence memories of new experiences}
\author{Jeremy R. Manning\textsuperscript{1, *}, Kirsten Ziman\textsuperscript{1, 2}, Emily Whitaker\textsuperscript{1},\\Paxton C. Fitzpatrick\textsuperscript{1}, Madeline R. Lee\textsuperscript{1}, and Andrew C. Heusser\textsuperscript{1, 3}\\\textsuperscript{1}Dartmouth College\\\textsuperscript{2}Princeton University\\\textsuperscript{3}Akili Interactive\\\textsuperscript{*}Corresponding author: jeremy.r.manning@dartmouth.edu}

\date{}
